\lightkurve: an open source Python package for NASA's \kepler, \ktwo~ and \tess~ data analysis

### 2018-04-09 paper/ms.tex
using minted

@@

        A \LightCurve~object can be instantiated by passing a \texttt{time}
        array, a \texttt{flux} array, and, optionally, a \texttt{flux\_err} array
        which accounts for uncertainties in the \texttt{flux} measurements, i.e.,
\begin{verbatim}
>>> from lightkurve import LightCurve
>>> lc = LightCurve(time, flux)
\end{verbatim}

@@

        Therefore, one can, for example, perform the following series of operations
        in order to fold a lightcurve from the MAST archive
\begin{verbatim}
>>> lc_file = KeplerLightCurveFile("kplr011904151-2009350155506_llc.fits")
>>> klc = lc_file.PDCSAP_FLUX.fold(period=0.837495)
>>> klc.plot()
\end{verbatim}

>>>>

\usepackage[cache=false]{minted}

@@

A \LightCurve~object can be instantiated by passing a \texttt{time}
array, a \texttt{flux} array, and, optionally, a \texttt{flux\_err} array
which accounts for uncertainties in the \texttt{flux} measurements, i.e.,
\begin{minted}{python}
>>> from lightkurve import LightCurve
>>> lc = LightCurve(time, flux)
\end{minted}

@@

Therefore, one can, for example, perform the following series of operations
in order to fold a lightcurve from the MAST archive
\begin{minted}{python}
>>> lc_file = KeplerLightCurveFile("kplr011904151-2009350155506_llc.fits")
>>> klc = lc_file.PDCSAP_FLUX.fold(period=0.837495)
>>> klc.plot()
\end{minted}
